Quantifying the overlap of ASVs between taxa

### 2020-10-28 exploratory/2020-10-21-asv-taxa-overlap.Rmd
Randomize subsampling 100 times using threshold of 1, closes #31

```{r}
# set RNG seed to Pat's birthday!
set.seed(19760620)
threshold <- 3

# metadata_asv - species - genome_id
subsample_species <- metadata_asv %>%
	select(genome_id, species) %>%
# return the distinct/unique rows
	distinct() %>%
# group_by the species
	group_by(species) %>%
# slice_sample on each species for N genomes
	slice_sample(n=threshold) %>%
	ungroup()

@@

# create a plot showing specificity at each taxonomic rank for each region
# x = taxonomic rank
# y = specificity or % of asvs found in more than one taxa
# geom = line plot
# different lines for each region of 16S rRNA gene
overlap_data %>%
	ggplot(aes(x=rank, y=overlap, group=region, color=region)) +
	geom_line()

overlap_data %>%
	filter(rank == "species") %>% kable
```

### Conclusions
* Sub regions are less specific at the species level than full-length. Still full-length has 3.6% overlap whereas the subregions are between 8.8 and 12.6% overlap
* This analysis does not control for uneven sampling of different species

>>>>

```{r}
# set RNG seed to Pat's birthday!
set.seed(19760620)

get_subsample_result <- function(threshold){
	# metadata_asv - species - genome_id
	subsample_species <- metadata_asv %>%
		select(genome_id, species) %>%
	# return the distinct/unique rows
		distinct() %>%
	# group_by the species
		group_by(species) %>%
	# slice_sample on each species for N genomes
		slice_sample(n=threshold) %>%
		ungroup()

@@

	return(overlap_data)
}

subsample_iterations <- map_dfr(1:100, ~get_subsample_result(threshold=1), .id="iterations")

summary_overlap_data <- subsample_iterations %>%
	group_by(region, rank) %>%
	summarize(mean_overlap = mean(overlap),
						lci = quantile(overlap, prob=0.025),
						uci = quantile(overlap, prob=0.975),
						.groups = "drop")

# create a plot showing specificity at each taxonomic rank for each region
# x = taxonomic rank
# y = specificity or % of asvs found in more than one taxa
# geom = line plot
# different lines for each region of 16S rRNA gene

summary_overlap_data %>%
	ggplot(aes(x=rank, y=mean_overlap, group=region, color=region, ymin=lci, ymax=uci)) +
	geom_linerange(show.legend=FALSE) + 
	geom_line()

summary_overlap_data %>%
	filter(rank == "species") %>% kable(digits=1)
```

### Conclusions
* Sub regions are less specific at every taxonomic rank than full-length sequences. Still full-length has 3.6% overlap whereas the sub-regions are between 10.2 and 15.0% overlap
